Optimal management of a stochastically varying population when policy adjustment is costly

### 2014-12-19 manuscripts/supplement.Rmd
update Dockerfile, tweak manuscript, separate out supplement

---
title: Optimal management of a stochastically varying population when policy adjustment is costly
author: 
  - name: Carl Boettiger
    affiliation: cstar
    email: cboettig (at) gmail.com
    footnote: Corresponding author
  - name: Michael Bode
    affiliation: melbourne
  - name: James Sanchirico
    affiliation: UCD
  - name: Jacob LaRiviere
    affiliation: UTK
  - name: Alan Hastings
    affiliation: UCD
  - name: Paul Armsworth 
    affiliation: UTK

address: 
  - code: cstar
    address: | 
      Center for Stock Assessment Research,
      110 Shaffer Rd,
      Santa Cruz, CA 95050, USA 
  - code: UCD
    address: Department of Environmental Science and Policy, University of California, Davis
  - code: melbourne
    address: University of Melbourne, Australia 
  - code: UTK
    address: University of Tennessee, Knoxville

@@

output:
  pdf_document:
    template: components/elsarticle.latex
    fig_caption: true

---

```{r configure, include=FALSE, cache=FALSE}
#source("components/install.R")

library("methods")
library("knitr")
basename <- "supplement"
opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
               cache.path = paste("components/cache/", basename, "/", sep=""))
opts_chunk$set(cache = 2)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
               comment = NA, verbose = TRUE, echo=FALSE)
# PDF-based figures
opts_chunk$set(dev='pdf')
fig.cache <- TRUE

library("rmarkdown")
library("pdgControl")
library("reshape2")
library("plyr")
library("ggplot2")
library("data.table")
library("pander")
library("cboettigR")
library("ggthemes")
library("snowfall")
library("tidyr")
library("dplyr")
transparent = theme(
    panel.background = element_rect(fill = "transparent",colour = NA), 
    plot.background = element_rect(fill = "transparent",colour = NA))

theme_set(theme_bw(base_size=18) + transparent)
```

```{r analysis, include=FALSE}
source("components/supp_analysis.R")
```

```{r ex_fish, fig.cap="", dev=c("pdf", "svg", "png"), dev.args=list(bg="transparent")}
ex <- filter(dt, replicate=="rep_17" & penalty_fn == "L1" & time < 20)
ggplot(ex) + 
  geom_line(aes(time, fishstock), col="darkblue", lwd=1)
```

## So then, do our optimal policies

```{r ex_harvest, fig.cap="", dev=c("pdf", "svg", "png"), dependson="ex_fish", dev.args=list(bg="transparent")}
ggplot(ex) + 
  geom_line(aes(time, harvest_alt), col="darkgreen", lwd=1) +
  ylab("Optimal quota policy") 
```

```{r, fig.cap="",  dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent"), fig.height=3}
ex <- dt %>% 
  filter(replicate=="rep_17" & penalty_fn == "L1" & time < 20) %>%
  select(time, fishstock, harvest_alt) %>%
  gather(variable, stock, -time) 
ggplot(ex) + 
  geom_line(aes(time, stock, col=variable), lwd=1) + 
  scale_color_discrete(labels=c(fishstock = "Stock size", harvest_alt = "Harvest policy"), name="")

@@

Apples to Apples
------------------

```{r Figure_2, fig.cap="",  dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}

relabel <- c(L1 = substitute(paste(Pi[1])),
             L2 = substitute(paste(Pi[2])),
             fixed = substitute(paste(Pi[3])))

ggplot(fees, aes(c2, (npv0-value)/npv0, color=variable)) + 
  geom_line(lwd=1) + 
  geom_hline(aes(yintercept=reduction), linetype=4) + 
  xlab("Penalty coefficient") +
  ylab("Reduction in net present value") + 
  scale_color_discrete(labels=relabel)

@@

```{r reex, fig.cap="", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent"), fig.height=3}
ggplot(ex) + 
  geom_line(aes(time, stock, col=variable), lwd=1) + 
  scale_color_discrete(labels=c(fishstock = "Stock size", harvest_alt = "Harvest policy"), name="") 
```

Quadratic Costs ($\Pi_2$)
-------------------------

```{r quadratic, fig.cap="", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
ex <- dt %>% 
  filter(replicate=="rep_17" & penalty_fn == "L2") %>%
  select(time, harvest, harvest_alt) %>%
  gather(variable, value, -time) 
ggplot(ex) + 
  geom_line(aes(time, value, col=variable), lwd=1) + 
  ylab("harvest quota") +
  scale_color_discrete(labels=c(harvest = "adjusted policy", harvest_alt = "baseline policy"), name="") 
```

Fixed Costs ($\Pi_3$)
---------------------

```{r fixed, fig.cap="", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
ex <- dt %>% 
  filter(replicate=="rep_17" & penalty_fn == "fixed") %>%
  select(time, harvest, harvest_alt) %>%
  gather(variable, value, -time) 
ggplot(ex) + 
  geom_line(aes(time, value, col=variable), lwd=1) + 
  ylab("harvest quota") +
  scale_color_discrete(labels=c(harvest = "adjusted policy", harvest_alt = "baseline policy"), name="") 
```

Linear Costs ($\Pi_1$)
---------------------

```{r linear, fig.cap="", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
ex <- dt %>% 
  filter(replicate=="rep_17" & penalty_fn == "L1") %>%
  select(time, harvest, harvest_alt) %>%
  gather(variable, value, -time) 
ggplot(ex) + 
  geom_line(aes(time, value, col=variable), lwd=1) + 
  ylab("harvest quota") +
  scale_color_discrete(labels=c(harvest = "adjusted policy", harvest_alt = "baseline policy"), name="") 
```

(For comparison)
----------------

```{r Figure_3, dependson="tidy", fig.cap="", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}

fig3_df <- as.data.frame(subset(dt, replicate=='rep_17'))
fig3_df <- fig3_df[c("time", "fishstock", "alternate", "harvest", "harvest_alt", "penalty_fn")]
fig3_df <- melt(fig3_df, id = c("time", "penalty_fn"))
fig3_df <- data.frame(fig3_df, baseline = fig3_df$variable)
variable_map <- c(fishstock = "fish_stock", alternate = "fish_stock", harvest = "harvest", harvest_alt = "harvest")
baseline_map <- c(fishstock = "penalty", alternate = "no_penalty", harvest = "penalty", harvest_alt = "no_penalty")
fig3_df$variable <- variable_map[fig3_df$variable]
fig3_df$baseline <- baseline_map[fig3_df$baseline]

harvest_fig3 <- subset(fig3_df, variable=="harvest")
fishstock_fig3 <- subset(fig3_df, variable=="fish_stock")

labeller <- function(variable,value){
    relabel[paste(value)]
}

ggplot(harvest_fig3, aes(time, value, col=baseline)) +
  geom_line(lwd=1) +
  facet_grid(penalty_fn~., labeller = labeller) + 
  labs(x="time", y="stock size", title = "Example Harvest Dynamics")  +
  scale_color_discrete(labels=c("Reed solution", "With penalty"), name="")
```

## General trends

```{r Figure_4, fig.cap="", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
ggplot(subset(figure4_df, statistic != "cross.correlation"), 
       aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn))  +
  stat_summary(fun.y = mean, 
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "ribbon", alpha=0.3, colour=NA) +
  stat_summary(fun.y = mean, geom = "line") + 
  coord_cartesian(xlim = c(0, .3)) + 
  facet_wrap(~ timeseries + statistic, scale="free_y") + 
  scale_color_discrete(labels=relabel, name="Penalty function") + 
  scale_fill_discrete(labels=relabel, name="Penalty function") + 
  xlab("Penalty size (as fraction of NPV0)")
```

- Quadratic ($\Pi_2$) smooths, Linear ($\Pi_1$) flattens, Fixed ($\Pi_3$) jumps

Consequences of policy adjustment costs 
---------------------------------------

```{r histogram-calc}
profits <- dt[, sum(profit_fishing), by=c('penalty_fn', 'replicate') ]
costs <- dt[, sum(policy_cost), by=c('penalty_fn', 'replicate') ]
reed_profits <- dt[, sum(profit_fishing_alt), by=c('penalty_fn', 'replicate') ]
reed_costs <- dt[, sum(policy_cost_alt), by=c('penalty_fn', 'replicate') ]
setnames(profits, "V1", "profits")
setnames(reed_profits, "V1", "profits")
Reed <- cbind(reed_profits, costs = reed_costs$V1, Assumption = "Reed") 
Adj <- cbind(profits, costs = costs$V1, Assumption = "Adjustment penalty")
hist_dat <- melt(rbind(Adj, Reed), id=c("penalty_fn", "replicate", "Assumption"))
````

```{r Figure_5, fig.cap="",  dependson="histogram-calc", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}

assume <- levels(as.factor(hist_dat$Assumption))
labeller <- function(variable,value){
if (variable=='penalty_fn') {
    return(relabel[paste(value)])
  } else {
    return(assume[value])
  }
}

@@

## To say that another way:

```{r Figure_6, fig.cap="", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}

who <- c("penalty_fn", "ignore_fraction", "assume_fraction", "reduction")
table1 <- arrange(error_df[who], reduction) 
names(table1) = c("penalty.fn", "ignoring", "assuming", "reduction")
table1_long <- melt(table1, id = c('penalty.fn', 'reduction'))
table1_long$reduction <- as.factor(table1_long$reduction)
table1_long <- subset(table1_long, reduction != "0.3")
ggplot(table1_long, aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + 
  facet_wrap(~reduction, ncol=2) + 
  scale_x_discrete(labels = c('L1' = substitute(paste(Pi[1])),
                              'L2' = substitute(paste(Pi[2])),
                              'fixed' = substitute(paste(Pi[3])))) + 
  xlab("Penalty function")
```

## Mismatches are even worse:

```{r Figure_7, fig.cap="", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
who <- c("penalty_fn", "ignore_fraction", "mismatched_fraction", "reduction")
table2 <- arrange(mismatches_df[who], reduction) 
names(table2) = c("penalty.fn", "ignoring", "mismatched", "reduction")
table2_long <- melt(table2, id = c('penalty.fn', 'reduction'))
table2_long$reduction <- as.factor(table2_long$reduction)

ggplot(table2_long, aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + 
  facet_wrap(~reduction, scales="free_y") +
  scale_x_discrete(labels = c('L1_L2' = substitute(paste(Pi[1],"_", Pi[2])), 
                              'L2_L1' =  substitute(paste(Pi[2],"_", Pi[1])),
                              'L1_fixed' = substitute(paste(Pi[1],"_", Pi[3])), 
                              'fixed_L1' =  substitute(paste(Pi[3],"_", Pi[1])),
                              'fixed_L2' = substitute(paste(Pi[3],"_", Pi[2])), 
                              'L2_fixed' =  substitute(paste(Pi[2],"_", Pi[3])))) + 
  xlab("Penalty function as: assumed_reality") + theme_tufte(base_size=14)
```

>>>>

---
title: Optimal management of a stochastically varying population when policy adjustment is costly
author: 
  - name: Carl Boettiger
    affiliation: cstar
    email: cboettig (at) gmail.com
    footnote: Corresponding author
  - name: Michael Bode
    affiliation: melbourne
  - name: James Sanchirico
    affiliation: UCD
  - name: Jacob LaRiviere
    affiliation: UTKEcon
  - name: Alan Hastings
    affiliation: UCD
  - name: Paul Armsworth 
    affiliation: UTKEEB

address: 
  - code: cstar
    address: | 
      Center for Stock Assessment Research,
      110 Shaffer Rd,
      Santa Cruz, CA 95050, USA 
  - code: UCD
    address: Department of Environmental Science and Policy, University of California, Davis
  - code: melbourne
    address: School of Botany, University of Melbourne, Australia 
  - code: UTKEEB
    address: Department of Ecology and Evolutionary Biology, University of Tennessee, Knoxville
  - code: UTKEcon
    address: Department of Economics, University of Tennessee, Knoxville

@@

output:
  pdf_document:
    template: components/elsarticle.latex
    fig_caption: true
---

\appendix

# Supplementary material #

##  Impact on the stock dynamics ##

Figure S1 shows the corresponding stock dynamics for the replicates illustrated in Figure 3 of the main text.  The impact of the adjustment cost on the stock dynamics is less dramatic than it is on the harvest dynamics, due to the stochastic growth in stock sizes and the sequence in which the steps are applied: stock values are assessed without error, then an optimal harvest is determined (using the pre-computed optimal policy based on both the stock assessment and the previous harvest, to account for possible adjustment costs), and then the stock that escapes harvesting recruits stochastically to set the population size for the next year.

Though this results in an effect that is less pronounced, the stock dynamics clearly reflect the same general trends observed in Figure 3: the quadratic costs ($\Pi_2$) show a clear smoothing of the variation in stock dynamics, while the fixed fee $\Pi_3$ results in exaggerated fluctionations in the stock sizes.  It is worth noting how changes in policy costs alone, such as introducing or rising fixed costs, can have important knock-on effects to population dynamics such as increased variance, a recent phenomenon observed in important fisheries that has recieved much attention elsewhere [@Anderson2008].

```{r StockDynamics, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=5, fig.width=8, cache = fig.cache, dev=c("pdf", "svg", "png")}

labeller <- function(variable,value){
    return(relabel[paste(value)])
}

dt_s <- dt %>% 
  filter(replicate=="rep_17" & time < 20) %>%
  select(time, fishstock, alternate, penalty_fn) %>%
  gather(variable, value, -time, -penalty_fn)

ggplot(dt_s, aes(time, value, col=variable, lty=variable)) +
  geom_line(lwd=1) +
  facet_grid(penalty_fn~., labeller = labeller) + 
  labs(x="time", y="stock size", title = "Example Stock Dynamics")  +
  scale_color_discrete(labels=c("With Penalty", "Reed Solution"), name="") +
  scale_linetype_discrete(labels=c("With Penalty", "Reed Solution"), name="")

@@

```{r StockStats, fig.cap="Variance and autocorrelation of stock dynamics, as a function of the penalty coefficient.  Adjustment penalty is calculated as percentage of the maximum expected $NPV$ in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}

stock_stats <- filter(figure4_df, timeseries=='stock')
ggplot(stock_stats, aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn)) + 
  stat_summary(fun.y = mean, 
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "ribbon", alpha=0.3, colour=NA) +
  stat_summary(fun.y = mean, geom = "line") + 
  coord_cartesian(xlim = c(0, .3)) + 
  facet_wrap(~ statistic, scale="free_y") + 
  scale_color_discrete(labels=relabel, name="Penalty function") + 
  scale_fill_discrete(labels=relabel, name="Penalty function") +
  xlab("Penalty size (as fraction of NPV0)")

@@

Recall that in our model definition, stock sizes are measured before harvest ($h_t$ being determined after observing stock size
$x_t$) and thus show less influence of the policy cost than the harvest itself.

## Additional stochastic realizations ##

Figure 3 of the main text shows a single stochastic realization.  Here we provide a sample of further realizations (including both stock and harvest dynamics).  Full

```{r Figure_S2, dependson="tidy", fig.cap="Multiple realizations of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=10, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png"), cache=FALSE}

labels <- c(harvest = substitute(paste("Harvest Policy under ", paste(Pi[1-3]))), 
            harvest_alt = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)")),
            fishstock = substitute(paste("Stock dynamics under under ", paste(Pi[1-3]))), 
            alternate = substitute(paste("Stock under ", paste(Pi[0]), " (Reed)")))
labeller <- function(variable,value){
if (variable=='penalty_fn') {
    return(relabel[paste(value)])
  } else {
    return(value)
  }
}

ex <- dt %>% 
  filter(replicate %in% paste0("rep_", 16:20) & time < 20) %>%
  select(time, fishstock, harvest, alternate, harvest_alt, replicate, penalty_fn) %>%
  gather(variable, stock, -time, -replicate, -penalty_fn)

ggplot(ex) + 
  geom_line(aes(time, stock, col=variable), lwd=1) + 
  scale_color_discrete(labels=labels, name="") +  
  facet_grid(replicate ~ penalty_fn, labeller=labeller)

write.csv(ex, "components/data/figure_s2.csv")
```

## Economic penalties using quadratic costs ##

```{r quadraticcosts}

source("components/quad_costs.R")
```

```{r Figure_S1, dev=c('pdf', 'svg'), cache=FALSE}

labels <- c(harvest = substitute(paste("Harvest Policy under ", paste(Pi[4]))), 
                                harvest_alt = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)")))

ex <- dt_quad %>% 
  filter(replicate=="rep_17" & time < 20) %>%
  select(time, harvest, harvest_alt) %>%
  gather(variable, stock, -time) 
ggplot(ex) + 
  geom_line(aes(time, stock, col=variable), lwd=1) + 
  scale_color_discrete(labels=labels, 
                       name="")

```{r quadshiftrate}
shifts <- dt[, fraction_no_shift(harvest), by=c("replicate")]
ave <- shifts[, mean(V1)]
```

Like the $\Pi_2$ adjustment cost based penalty, this quadratic cost based penalty shows periods of contant, strictly positive policy only `r ave * 100`% of the time, and exhibits the same kind of smoothing of more small adjustments that is seen in $\Pi_2$ scenario.

Ignoring adjustment costs is worst than wrongly assuming adjustment costs
--------------------------------------------------------------------------

Figure S3 extends Figure 5 of the main text across all three functional forms of adjustment costs, $\Pi_{1-3}$. To reduce overplotting of Figure 5 we have also separated the distributions of dockside revenue and adjustment fees by scenario, such that the top row shows the distributions when the policy accounts for adjustment costs, and the bottom shows the policy when it does not (that is, the original @Reed1979 model applied to the scenario of costly adjustment).

```{r Figure_S3, fig.cap="Distribution of profits from fishing and costs paid to adjustment.  Distributions are shown when managing a system in which the adjustment costs present are determined by the model indicated, and compared to the same costs and profits of managing the same system using a Reed model, which ignores adjustment costs, and thus tends to pay much higher fees for adjustment.  In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).", fig.width=8, fig.height=6, dependson="histogram-calc", dev=c("pdf", "svg", "png"), cache=FALSE}

assume <- levels(as.factor(hist_dat$Assumption))
labeller <- function(variable,value){
if (variable=='penalty_fn') {
    return(relabel[paste(value)])
  } else {
    return(paste(value))
    #return(assume[paste(value)])
  }
}

@@

write.csv(hist_dat, "components/data/figure5.csv")
```

Figure S4 extends the results shown in Figure 6 across different severities of adjustment cost, totalling from 10% up to 25% of the NPV of the stock. While the same qualitative pattern is observed in all cases, it is strongest in the higher penalties.

```{r Figure_S4, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue), shown by penalty function over increasing magnitudes of cost.  All values are relative to the cost-free adjustment optimum, NPV0.  In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present. The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs.", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}

ggplot(table1_long, aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + 
  facet_wrap(~reduction, ncol=2) + 
  scale_x_discrete(labels = c('L1' = substitute(paste(Pi[1])),
                              'L2' = substitute(paste(Pi[2])),
                              'fixed' = substitute(paste(Pi[3])))) + 
  xlab("Penalty function")
write.csv(table1_long, "components/data/figureS4.csv")
```

Mismatched penalty functions
----------------------------

When policy costs are present, assuming the wrong functional form may or
may not be worse than ignoring the presence of policy costs all together.
Figure S5 considers several such cases.  The X axis labels indicate
first which policy is being used to drive the harvest decisions, and
then which penalty is actually being applied.  Thus $\Pi_1\_\Pi_2$ indicates
a policy calculated under the linear ($\Pi_1$) costs, when the reality
involves quadratic ($\Pi_2$) costs.  Though the coefficients of the ($\Pi_2$)
costs have been scaled such that the net effect is the same, the inferred
policies differ.  As a result, the value is slightly more than half of
the optimal free solution when the expected reduction should only be 10% (panel A)
less than optimal free based on the $c_i$ calibration. In this case, ignoring the costs all together
is still worse than using $\Pi_1$ costs -- the red bar is lower than the blue.

For fixed costs ($\Pi_3$), the reverse is true.  Because fixed costs increase the
volatility of the optimal solution while $\Pi_2$ costs decrease it, simply
ignoring the cost of adjustment all together results in a higher value
than either assuming costs are quadratic ($\Pi_2$) when they are fixed ($\Pi_3$),
or assuming they are fixed when they are quadratic.  Scenarios in which true costs are quadratic (regardless of what
cost structure is assumed by the policy) do significantly worse than
those that are not (i.e. all cases that assume quadratic but actually
have linear or fixed costs).

```{r Figure_S5, fig.cap="Mismatches. X axis labels indicate the model used to derive the policy, followed by the model used to simulate the penalty. Blue bars show the net present value of that scenario.  Compare to red bars, which show the consequence of using a policy that ignores costs all together in the same scenario (i.e. costs as indicated by second code), rather than assuming the policy indicated by the first code in the pair.  All values are scaled to a fraction of the adjustment free net present value.", dev=c("pdf", "svg", "png"), fig.width=7}
who <- c("penalty_fn", "ignore_fraction", "mismatched_fraction", "reduction")
table2 <- arrange(mismatches_df[who], reduction) 
names(table2) = c("penalty.fn", "ignoring", "mismatched", "reduction")
table2_long <- melt(table2, id = c('penalty.fn', 'reduction'))
table2_long$reduction <- as.factor(table2_long$reduction)

ggplot(filter(table2_long, reduction==0.25), 
  aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + 
  facet_wrap(~reduction, scales="free_y") +
  scale_x_discrete(labels = c('L1_L2' = substitute(paste(Pi[1],"_", Pi[2])), 
                              'L2_L1' =  substitute(paste(Pi[2],"_", Pi[1])),
                              'L1_fixed' = substitute(paste(Pi[1],"_", Pi[3])), 
                              'fixed_L1' =  substitute(paste(Pi[3],"_", Pi[1])),
                              'fixed_L2' = substitute(paste(Pi[3],"_", Pi[2])), 
                              'L2_fixed' =  substitute(paste(Pi[2],"_", Pi[3])))) + 
  xlab("Penalty function")
write.csv(table2_long, "components/data/figureS5.csv")
```

These patterns hold across the different size reductions shown (from 10%
to 25%, Figure S6 panels a-d respectively), though net present value becomes negative under the quadratic
form for the larger penalties as costs paid for adjustments exceed
profits derived from harvest.  (Though optimal solutions will always
avoid negative net present values, these scenarios in which policies are
applied under conditions other than assumed in the optimality calculation
have no such guarantee.) For each scenario, results are averaged over
100 replicates.

```{r Figure_S6, fig.cap="Effect of varying severity of adjustment costs on mismatches. Successive panels show increasing reduction of the net present value by increasing penalty coefficients: e.g. a policy in the first panel would lose only 10% (panel A) of its net present value to adjustment costs if it had the correct form of those costs, as determined by the choice of penalty coefficient.  Plots structured as in figure 7, which corresponds to the fourth panel", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}
ggplot(table2_long, aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + 
  facet_wrap(~reduction, scales="free_y") +
  scale_x_discrete(labels = c('L1_L2' = substitute(paste(Pi[1],"_", Pi[2])), 
                              'L2_L1' =  substitute(paste(Pi[2],"_", Pi[1])),
                              'L1_fixed' = substitute(paste(Pi[1],"_", Pi[3])), 
                              'fixed_L1' =  substitute(paste(Pi[3],"_", Pi[1])),
                              'fixed_L2' = substitute(paste(Pi[3],"_", Pi[2])), 
                              'L2_fixed' =  substitute(paste(Pi[2],"_", Pi[3])))) + 
  xlab("Penalty function")
```
